%-------------------------
% Resume in Latex
% Author: Sk Ajimuddin
%------------------------

\documentclass[letterpaper,11pt]{article}
% \documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-6pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

%----------Heading----------
\begin{center}
    {\Huge \scshape Sk Ajimuddin} \\ \vspace{4pt}
    \small 
    \href{tel:+918328939820}{\faPhone\ \underline{+91 83289 39820}} ~ 
    \href{mailto:skazimdev@gmail.com}{\faEnvelope\ \underline{skazimdev@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/skajimuddin/}{\faLinkedin\ \underline{linkedin.com/in/skajimuddin}} ~
    \href{https://github.com/skajimuddin}{\faGithub\ \underline{github.com/skajimuddin}}
\end{center}


%-----------Summary-----------
\section{Summary}
Full-Stack Software Engineer with 2+ years of experience across freelance and full-time roles, architecting scalable systems and delivering high-impact business solutions. Specialties include full-stack web architecture and integrating AI-assisted workflows to improve productivity, code quality, and overall delivery speed.

%-----------Experience-----------
\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {Data Analyst Intern}{April 2025 -- June 2025}
    {Dataview Analytics (Remote)}{Tools Used: Excel, SQL, Power BI}
    \resumeItemListStart
      \resumeItem{\textbf{Processed and standardized a dataset of over 1,00,000 rows} from multiple regions to support weekly analytics—enabled business teams to track KPIs across geography and time.}
      \resumeItem{Designed smart Excel templates embedded with lookup functions and pivot logic, \textbf{saving 40\% reporting time across 4 departments.}}
      \resumeItem{Developed and maintained Power BI dashboards to visualize revenue trends, customer mix, and monthly performance—regularly used by managers and analysts across business units.}
      \resumeItem{Collaborated with 4 analysts and 2 senior managers to define and validate 6 KPIs, improving report reliability and strategic alignment.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------Experience-----------
\section{Experience}
\resumeSubHeadingListStart

  \resumeProjectHeading
      {\textbf{Software Developer} $|$ \emph{ASR Hospitals (India) Private Limited, Agartala, Tripura}}{Oct 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Developing a Laboratory Management System with role-based access control for lab technicians, doctors, and administrators, ensuring secure and structured workflows.}
        \resumeItem{Building a responsive frontend using React and Tailwind CSS, and designing backend services with Node.js, Express, and Go-based microservices for scalability and performance.}
      \resumeItemListEnd

  \resumeProjectHeading
      {\textbf{Software Developer} $|$ \emph{ASTU Creatives Agency, Pune, Maharashtra}}{Aug 2024 -- Aug 2025}
      \resumeItemListStart
        \resumeItem{Developed and maintained dynamic web applications using the MERN stack, ensuring high performance and scalability.}
        \resumeItem{Integrated Razorpay, Gemini API, Firebase, PWA, and AI-powered chatbot features to enhance functionality, payments, real-time data syncing, and customer support.}
        \resumeItem{Deployed applications on AWS Lambda, Hostinger, and Firebase, ensuring cost-effective, scalable, and reliable hosting solutions.}
      \resumeItemListEnd

  \resumeProjectHeading
      {\textbf{Freelance Developer \& Founder} $|$ \emph{Zeonweb.com}}{}
      \resumeItemListStart
        \resumeItem{Built Zeonweb.com, a digital agency delivering web development, app development, AI-powered solutions, automation tools, and ongoing maintenance.}
        \resumeItem{Designed and delivered full-stack websites and applications for clients, covering UI/UX, backend development, deployment, and long-term support.}
      \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------Projects-----------
\section{Key Projects}
\resumeSubHeadingListStart
  \resumeProjectHeading
      {\textbf{Customer Churn Analysis} $|$ \emph{Python }}{March 2025 -- April 2025}
      \resumeItemListStart
        \resumeItem{\textbf{Analyzed behavior of 7,043 telecom customers} to identify churn patterns based on tenure, contract type, and monthly charges.}
        \resumeItem{Engineered new features including contract type buckets and tenure bands to improve segmentation and insights.}
        \resumeItem{Generated 11 visualizations (histograms, box plots, heatmaps) to highlight churn-prone segments.}
        \resumeItem{Revealed that 38\% of churned users were on monthly contracts with less than 3-month tenure—suggested early engagement strategies.}
      \resumeItemListEnd
  \resumeProjectHeading
      {\textbf{Sales Dashboard for Regional Performance} $|$ \emph{SQL, Power BI}}{February 2025 -- March 2025}
      \resumeItemListStart
        \resumeItem{Queried and joined 3 sales-related tables covering over 25,000 rows across 12 months and 5 regions using optimized SQL joins to create consistent, analysis-ready datasets.}
        \resumeItem{Built 10 dynamic measures and KPIs in Power BI to track regional sales, return trends, and product performance.}
        \resumeItem{Designed multipage dashboards with slicers and filters, helping stakeholders drill down by region, product category, and time.}
        \resumeItem{Detected a 14\% sales drop post-festival in the South region. Later, the insight was used for a marketing recovery plan.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------
\section{Key Certifications}
\resumeItemListStart
  \resumeItem{\href{https://www.udemy.com/certificate/UC-689a510e-ba1f-4bde-a747-4dcb60be473f/}{\textbf{Complete Web Development Course – Udemy:}} Completed 100+ hours of coursework. built and deployed scalable full-stack applications using the MERN stack, Next.js, Tailwind CSS, PostgreSQL, and Prisma.}
  \vspace{-5pt}
  \resumeItem{\href{https://scrimba.com/certificate-cert2uNjfK9m1uNZ5v8RvYFqLcn2NxZ2keLE9bE}{\textbf{Frontend Developer Career Path – Scrimba:}} Completed 80+ hours of interactive coding. built dynamic, real-world applications focused on accessibility, responsive UI, API integrations, and advanced React.}
\resumeItemListEnd

%-----------SKILLS-----------
\section{Skills}
\textbf{Front-End:} HTML5, CSS3, JavaScript (ES6+), React, TypeScript, Tailwind CSS, Shadcn UI  \\
\textbf{Back-End:} Node.js, Express, Fastify, SQL, MongoDB, REST APIs, Firebase \\
\textbf{Tools \& Technologies:} Git, Postman, Linux, AI Tools, AWS

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Bachelor of Computer Applications (BCA)}{Graduated: 2025}
    {DRIEMS University, Tangi, Odisha}{CGPA: 8.3 / 10}
\resumeSubHeadingListEnd

\end{document}
