%-------------------------
% Resume in Latex
% Author: Sk Ajimuddin
%------------------------

% \documentclass[letterpaper,11pt]{article}
\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1
\pdfglyphtounicode{phone}{0020}
\pdfglyphtounicode{envelope}{0020}
\pdfglyphtounicode{linkedin}{0020}
\pdfglyphtounicode{github}{0020}
\pdfglyphtounicode{external-link-alt}{0020}

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \ifx&#3&%
      \else
        \textit{\small #3} & \textit{\small #4} \\
      \fi
    \end{tabular*}\vspace{-6pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & \textbf{\small #2}\\
  \end{tabular*}\vspace{-6pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

%----------Heading----------
\begin{center}
  {\Huge \scshape Sk Ajimuddin} \\ \vspace{4pt}
  \small
  \href{tel:+918328939820}{\faPhone\ \underline{+91 83289 39820}} ~|~
  \href{mailto:skazimdev@gmail.com}{\faEnvelope\ \underline{skazimdev@gmail.com}} ~|~
  \href{https://www.linkedin.com/in/skajimuddin/}{\faLinkedin\ \underline{linkedin.com/in/skajimuddin}} ~|~
  \href{https://github.com/skajimuddin}{\faGithub\ \underline{github.com/skajimuddin}}
\end{center}

%-----------Summary-----------
\section{Summary}
Full-Stack Software Engineer with \textbf{2+ years} of experience across freelance and full-time roles, architecting scalable systems and delivering high-impact business solutions. Specialties include full-stack web architecture and integrating AI-assisted workflows to improve productivity, code quality, and overall delivery speed.

%-----------Experience-----------
\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {\textbf{Software Engineer} $|$ {\normalfont\textit{ASR Hospitals (India) Private Limited, Agartala}}}{Nov 2025 -- Apr 2026}
    {}{}
    \resumeItemListStart
      \resumeItem{Built and integrated back-end APIs and front-end UIs for a laboratory management system using \textbf{React, Node.js, Express, and PostgreSQL}, ensuring best practices throughout the development lifecycle.}  
      \resumeItem{Refactored the codebase into a structured \textbf{MVC architecture} and redesigned the database schema, improving system scalability, maintainability, and performance by \textbf{2x}.}
      \resumeItem{Researched and developed a Laboratory Information System (LIS) by building a Node.js \textbf{TCP/IP server} for connecting lab analyzers and automating data synchronization with the database, reducing manual work.}
    \resumeItemListEnd

  \resumeSubheading
    {\textbf{Full-Stack Developer} $|$ {\normalfont\textit{ASTU Creatives Agency, Pune}}}{Aug 2024 -- Sep 2025}
    {}{}
    \resumeItemListStart
      \resumeItem{Built and delivered full-stack web applications for multiple clients using the \textbf{MERN stack}, handling both front-end and back-end development with a focus on scalability and production-ready systems.}
      \resumeItem{Integrated \textbf{payment systems, AI APIs, real-time features, and Progressive Web App (PWA)} capabilities to enhance overall application functionality and user experience.}
      \resumeItem{Deployed and maintained applications across \textbf{AWS and other cloud platforms}, ensuring reliable performance, scalable infrastructure, and smooth maintenance throughout the lifecycle.}
  \resumeItemListEnd

  \resumeSubheading
    {\textbf{Freelance Developer}}{Feb 2024 -- Aug 2024}
    {}{}
    \resumeItemListStart
      \resumeItem{Designed, developed, and deployed \textbf{full-stack} applications for clients, handling front-end, back-end, and production deployment across multiple projects.}
      \resumeItem{Delivered custom software solutions including \textbf{business management systems, billing tools, automation solutions, and AI-powered tools} based on client requirements.}
      \resumeItem{Built \textbf{cross-platform} applications, including Electron desktop apps and Android apps, expanding development beyond web platforms.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------Projects-----------
\section{Key Projects}
\resumeSubHeadingListStart
  \resumeSubheading
    {\textbf{Restaurant Management System}}{}
    {}{}
    \resumeItemListStart
      \resumeItem{Built a \textbf{full-stack} restaurant management system with \textbf{order, menu, and billing} features, supporting \textbf{multiple roles} (admin, waiter, kitchen) with \textbf{real-time updates} across devices using \textbf{SSE} over a local network.}
      \resumeItem{Deployed the application locally using \textbf{NSSM} for multi-device access within the restaurant network, currently handling \textbf{300+ orders/week} in a live production environment.}
    \resumeItemListEnd

  \resumeSubheading
    {\textbf{\href{https://the-anonify.netlify.app/}{Anonify – Anonymous Social Media Platform {\scriptsize\faIcon{external-link-alt}}}}}{}
    {}{}
    \resumeItemListStart
      \resumeItem{Developed a privacy-focused PWA using \textbf{React, TypeScript, Node.js, Express.js, and MongoDB} with secure \textbf{JWT + OTP} authentication, dynamic slang word filtering, and an admin panel.}
      \resumeItem{Integrated \textbf{AI-powered grammar correction}, \textbf{emoji suggestions}, and keyword-based trending detection.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------
\section{Key Certifications}
\resumeSubHeadingListStart
  \resumeItem{\href{https://www.udemy.com/certificate/UC-689a510e-ba1f-4bde-a747-4dcb60be473f/}{\textbf{Complete Web Development Course} {\scriptsize\faIcon{external-link-alt}}} -- \textbf{Udemy:} Completed 100+ hours of coursework. Built and deployed scalable full-stack applications using the MERN stack, Next.js, Tailwind CSS, PostgreSQL, and Prisma.}
  % \vspace{-5pt}
  \resumeItem{\href{https://scrimba.com/certificate-cert2uNjfK9m1uNZ5v8RvYFqLcn2NxZ2keLE9bE}{\textbf{Frontend Developer Career Path} {\scriptsize\faIcon{external-link-alt}}} -- \textbf{Scrimba:} Completed 80+ hours of interactive coding. Built dynamic, real-world applications focused on accessibility, responsive UI, API integrations, and advanced React.}
\resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
\textbf{Front-End:} HTML5, CSS3, JavaScript (ES6+), React, TypeScript, Tailwind CSS, shadcn/ui \\
\textbf{Back-End:} Node.js, Express, Fastify, SQL, MongoDB, REST APIs, Firebase \\
\textbf{Tools \& Technologies:} Git, Postman, Linux, AI tools, AWS

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Master of Computer Applications (MCA)}{2025 -- Present}
    {Global Institute of Management - Bhubaneswar, Odisha}{}
  \resumeSubheading
    {Bachelor of Computer Applications (BCA)}{Graduated: 2025}
    {DRIEMS University - Tangi, Odisha}{CGPA: 8.3 / 10}
\resumeSubHeadingListEnd

\end{document}
